---
title: "Democrats vs Republicans"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---


In this study, I focus on U.S. Presidential inauguration speeches of 8 presidents in the recent 50 years . Here I conduct a brief comparison of speeches by the parties to which the presidents stand for. I am interested in the similarities and the difference of the speeches in terms of length and content.

```{r,echo = FALSE, warning=FALSE}
#Load Libraries
library("tm")
library("SnowballC")
library("wordcloud")
library("rvest")
library("tibble")
library("qdap")
library("sentimentr")
library("gplots")
library("dplyr")
library("tm")
library("syuzhet")
library("factoextra")
library("beeswarm")
library("scales")
library("RColorBrewer")
library("RANN")
library("tm")
library("topicmodels")
library("xlsx")
library("plotrix")
library("formattable")
library("ggplot2")
```


```{r, echo = FALSE, warning=FALSE}
#Load Speeches
setwd("/Users/JingyiWang/Google Drive/5243 Data/GitHub")

files <- c("../data/InauguralSpeeches/inaugRichardNixon-1.txt", 
           "../data/InauguralSpeeches/inaugRichardNixon-2.txt",
           "../data/InauguralSpeeches/inaugJimmyCarter-1.txt",
           "../data/InauguralSpeeches/inaugRonaldReagan-1.txt",
           "../data/InauguralSpeeches/inaugRonaldReagan-2.txt",
           "../data/InauguralSpeeches/inaugGeorgeBush-1.txt",
           "../data/InauguralSpeeches/inaugWilliamJClinton-1.txt",
           "../data/InauguralSpeeches/inaugWilliamJClinton-2.txt",
           "../data/InauguralSpeeches/inaugGeorgeWBush-1.txt",
           "../data/InauguralSpeeches/inaugGeorgeWBush-2.txt",
           "../data/InauguralSpeeches/inaugBarackObama-1.txt",
           "../data/InauguralSpeeches/inaugBarackObama-2.txt",
           "../data/InauguralSpeeches/inaugDonaldJTrump-1.txt")
speech1=paste(readLines(files[1], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech2=paste(readLines(files[2], 
                  n=-1, skipNul=TRUE),collapse=" ")

speech3=paste(readLines(files[3], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech4=paste(readLines(files[4], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech5=paste(readLines(files[5], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech6=paste(readLines(files[6], 
                  n=-1, skipNul=TRUE),collapse=" ")

speech7=paste(readLines(files[7], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech8=paste(readLines(files[8], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech9=paste(readLines(files[9], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech10=paste(readLines(files[10], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech11=paste(readLines(files[11], 
                  n=-1, skipNul=TRUE),collapse=" ")
speech12=paste(readLines(files[12], 
                  n=-1, skipNul=TRUE),collapse=" ")

speech13=paste(readLines(files[13], 
                  n=-1, skipNul=TRUE),collapse=" ")



#Full dataframe 
inaug <- read.csv("../output/InaugurationInfo.csv",stringsAsFactors = FALSE)

inaug$Fulltext <- c(speech1,speech2,speech3,speech4,speech5,speech6,speech7,speech8,
                    speech9,speech10,speech11,speech12,speech13)

inaug$Words <-word_count(inaug$Fulltext)
inaug$Date = as.Date(inaug$Date , "%m/%d/%y")
```

### List of Presidents of United States from  1969 to 2018

```{r,echo =FALSE,warning=FALSE}
#Presidents and their parties dataframe 
President.party<- data.frame(id = 1:8,
  President = unique(inaug$President),
                             Presidency =c("1969-1974","1977-1981","1981-1989","1989-1993","1993-2001","2001-2009","2009-2017"," 2017-Incumbent"),
                             Party = c("Republican","Democratic","Republican","Republican","Democratic","Republican","Democratic","Republican"))
library("formattable")
formattable(President.party, list(
  President = formatter("span", style= style(font.weight = "bold")),
  Presidency = formatter("span", style = style(font.weight = "bold")),
  Party = formatter("span", style = x ~ ifelse(x == "Republican", style(color = "#E31A1C", font.weight = "bold"), style(color = "#1F78B4", font.weight = "bold")))
))




```



###Part 1. Length of the Inaugural Addresses

In the recent 40 years, the average number of words used by each president fluctuate between 1200 to 2500.It seems like presidents of the Democratic Party delivered slightly shorter speeches, but the difference is not significant.Presidents known to have good public - speaking techniques, such as Ronald Reagan and Barack Obama, gave longer speeches.

```{r,echo = FALSE, warning=FALSE,fig.width = 3, fig.height = 2}
ave.words = inaug %>% group_by(File) %>% summarise(mean_word = mean(Words))
President.party$Ave.Words  <- ave.words$mean_word
President.party$President = factor(President.party$President,levels = President.party$President)

library("ggplot2")
 ggplot(President.party,aes(fill = Party, y = Ave.Words, x = factor(President))) +
    geom_bar(position="dodge", stat="identity",width=0.5)+
   scale_fill_manual(values=c("#1F78B4", "#E31A1C")) + 
  theme(axis.text.x=element_text(angle=60, hjust=1,color="#993333",face="bold"))+
  labs(title = "Number of Words of Inaugural Speeches ", x= "President",y  ="Word Count",size = 3) 
```



```{r,echo = FALSE, warning=FALSE}
#Candidates
rep.candidates <- unique(inaug[inaug$Party == "Republican",]$File)
dem.candidates <-  unique(inaug[inaug$Party == "Democratic",]$File)

#Seperate dataframe for 2 parties
rep.df = filter(inaug, File %in% rep.candidates)
dem.df = filter(inaug, File %in% dem.candidates)

#Seperate speeches
docs <- Corpus(VectorSource(inaug$Fulltex)) 
rep.docs<-Corpus(VectorSource(rep.df$Fulltext)) 
dem.docs<-Corpus(VectorSource(dem.df$Fulltext)) 

#Text Cleaning function 

timeword <- c("mon", "tue", "wed", "fri", "sat", "monday", "tuesday", "wednesday", "thursday", "friday", "saturday", "sunday", "subject", "sent", "january", "february", "march", "april", "may", "june", "july", "august", "september", "november", "december", "october", "one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten")

clean <- function(text){
  text <-tm_map(text,content_transformer(tolower))
  text <- tm_map(text, removePunctuation)
  text <- tm_map(text, removeNumbers)
  text <- tm_map(text, removeWords, stopwords("english"))
  text <- tm_map(text, stripWhitespace)
  text <- tm_map(text,stemDocument)
  text <- tm_map(text, removeWords,c("will","now","can", "may", "upon", "shall", "will","must"))
  text <- tm_map(text, removeWords,timeword)
  text <- tm_map(text, content_transformer(function(x) gsub(x, pattern = "us", replacement = "america")))
  text <- tm_map(text, content_transformer(function(x) gsub(x, pattern = "countri", replacement = "nation")))
  text <- tm_map(text, content_transformer(function(x) gsub(x, pattern = "respon", replacement = "respons")))
  text <- tm_map(text, removeWords,c("make","let","live","today","day"))
  return(text)
}

docs <- clean(docs)
rep.docs <- clean(rep.docs)
dem.docs <- clean(dem.docs)


#Make a term-document matrix
dtm = TermDocumentMatrix(docs)
rep.dtm <- TermDocumentMatrix(rep.docs)
dem.dtm <- TermDocumentMatrix(dem.docs)

#Make seperate term matrices for 2 parties
rep.matrix<- as.matrix(rep.dtm)
rep.matrix = rep.matrix[order(rowSums(rep.matrix),decreasing=TRUE),]
rep.wordfreq <- data.frame(terms = rownames(rep.matrix),
 frequency = rowSums(rep.matrix));rownames(rep.wordfreq) <- 1:nrow(rep.wordfreq)

dem.matrix<- as.matrix(dem.dtm)
dem.matrix = dem.matrix[order(rowSums(dem.matrix),decreasing=TRUE),]
dem.wordfreq <- data.frame(terms = rownames(dem.matrix),
 frequency = rowSums(dem.matrix));rownames(dem.wordfreq) <- 1:nrow(dem.wordfreq)

```


### Part 2. Textual Analysis
In the text cleaning process, besides the usual procedure, I manually removed some uninformative words such as will, can, and let and replaced some synonyms. After that, I plot word clouds of the most frequently used 100 words for presidents of 2 Parties and look at their similarity.


#####a.Republican
```{r,echo = FALSE, warning=FALSE,fig.width = 3, fig.height = 1.5}
library("wordcloud")
wordcloud(words = rep.wordfreq$terms, freq = rep.wordfreq$frequency, 
          max.words = 100, colors = brewer.pal(8, "Dark2"), 
          random.order=FALSE, rot.per=0.35)
```

####b.Democratic
```{r,echo = FALSE, warning=FALSE,fig.width = 3, fig.height = 1.5}
library("wordcloud")
wordcloud(words = dem.wordfreq$terms, freq = dem.wordfreq$frequency, 
          max.words = 100, colors = brewer.pal(8, "Dark2"), random.order=FALSE, rot.per=0.35, )

```



#####c. Top 20 Words shared by Presidents of Two Parties
```{r,echo = FALSE, warning=FALSE,fig.width = 3.5, fig.height = 2}
all_text <- c(paste(rep.df$Fulltext, collapse = ""), paste(dem.df$Fulltext,collapse = ""))
all_text <- Corpus(VectorSource(all_text))
all_text_dtm <-clean(all_text)
all_text_dtm <- TermDocumentMatrix(all_text_dtm)
# inspect(all_text_dtm)
colnames(all_text_dtm) <- c("Republican", "Democratic")
all_text_matrix <- as.matrix(all_text_dtm)



shared <- subset(all_text_matrix, all_text_matrix[,1]>=0 &all_text_matrix[,2]>=0)
#Sort shared words: most common to least common 
diff <- abs(shared[, 1] - shared[, 2])
shared_matrix <- cbind(shared, diff)
shared_matrix <- shared_matrix[order(shared_matrix[, 3],decreasing = TRUE), ]
shared.top20 <- data.frame(Republican = shared_matrix[1:20, 1],
                           Democratic = shared_matrix[1:20, 2],
                           terms = rownames(shared_matrix[1:20, ]))


 pyramid.plot(shared.top20$Republican,shared.top20$Democratic, labels = shared.top20$terms,
 main = "Top 20 Words in Common",space = 0.5, gap = 40,raxlab = NULL, unit = NULL, top.labels = c("Republican","Words","Democratic"))

```
The most frequent words shared are America, people, world, nation, government, etc. This is expected because inaugural addresses are used to present presidents' visions and goals for the country, their promises to the people, and the missions for the government. Words like peace, freedom are long-term goals that could not be emphasized enough. 
Here I am interested in the word history and want to know its context.So I found 10 words that are most correlated to the word history,and it seems like when the presidents look back in history,they care about aid they received, wins, threatens to lives of the people, and rebuilding the country.

```{r,echo = FALSE}
cat("Words associated with the word hisotry")
history <- findAssocs(dtm, terms = "histor", 0.2)$histor[1:10];history
```


####d. Comparison cloud of top 50 words that appear in speeches from one party but not the other

```{r,echo = FALSE, warning=FALSE,fig.width = 3, fig.height = 1.5}
comparison.cloud(all_text_matrix,
 colors = c("#E31A1C", "#1F78B4"),
 max.words = 50)
```
Code from https://s3.amazonaws.com/assets.datacamp.com/production/course_935/ch2_pdf_slides.pdf


```{r,echo = FALSE, warning = FALSE}
#Let's look at frequent term  for 2 parties
set.seed(15)
rep.frequent.terms <- freq_terms(rep.docs,
           top= 55, 
          at.lease = 10,
          stopwords = "Top200Words")
set.seed(15)
dem.frequent.terms <- freq_terms(dem.docs,
           top= 50, 
          at.lease = 10,
          stopwords = "Top200Words")

rep.only <- setdiff(rep.frequent.terms$WORD,dem.frequent.terms$WORD)
dem.only <- setdiff(dem.frequent.terms$WORD,rep.frequent.terms$WORD)
dem.only <- dem.only[-c(7,12,8,11,15,17,18,27,28,29)]


cat("Republican: ",rep.only)
```

```{r,echo = FALSE}
cat("Democratic: ",dem.only)
```
It seems like presidents from different parties differ in philosophies. Presidents from the Democratic Party talk more about equality & health care, children land issues. Whereas presidents from the Republican party talks more about freedom, housing policies, state, and union. The findings matche two parties' long term ideology. 



####e. Closer look at some ambiguous words and its syntax
Here again, I found the 10 words that are most correlated with the word "never" which appear very often in speeches from the Republican Party but not from the Democratic Party. "Never" which is associated with negative sentiments is related to immigration. 
For presidents of the Democratic Party, the word "future"  is associated with dignity and school which is consistant with their political stands.
```{r,echo = FALSE,warnings = FALSE}
#Find Frequent words and their associations
never <- findAssocs(rep.dtm, terms = "never", 0.2)$never[1:10]
never
```

```{r,echo = FALSE,warnings = FALSE}
futur <- findAssocs(dem.dtm, terms = "futur", 0.2)$futur[1:10];futur

```


### Part 2. Topics Modeling of Inaugural Speeches
I did LDA on inaugural speeches for all U.S presidents and take a close look at the 8 presidents we are interested in. We study how often presidents address seven topics: Economy , Equality, Misc, Legislation, Government, Reform,Freedom. In the plot of the average frequency presidents adresse those 7 topics, it seems like there is only subtle difference between parties.Republicans address freedom and government slightly more often than Democrats which is consistent from our findings before.


```{r, message=FALSE, warning=FALSE}
packages.used=c("rvest", "tibble", "qdap", 
                "sentimentr", "gplots", "dplyr",
                "tm", "syuzhet", "factoextra", 
                "beeswarm", "scales", "RColorBrewer",
                "RANN", "tm", "topicmodels")

# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

# load packages
library("rvest")
library("tibble")
library("topicmodels")
source("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/lib/plotstacked.R")
source("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/lib/speechFuncs.R")

main.page <- read_html(x = "http://www.presidency.ucsb.edu/inaugurals.php")
inaug=f.speechlinks(main.page)
inaug=inaug[-nrow(inaug),] # remove the last line, irrelevant due to error.
main.page=read_html("http://www.presidency.ucsb.edu/nomination.php")
nomin <- f.speechlinks(main.page)
nomin <- nomin[-47,]
main.page=read_html("http://www.presidency.ucsb.edu/farewell_addresses.php")
farewell <- f.speechlinks(main.page)

inaug.list=read.csv("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/data/inauglist.csv", stringsAsFactors = FALSE)
nomin.list=read.csv("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/data/nominlist.csv", stringsAsFactors = FALSE)
farewell.list=read.csv("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/data/farewelllist.csv", stringsAsFactors = FALSE)

speech.list=rbind(inaug.list, nomin.list, farewell.list)
speech.list$type=c(rep("inaug", nrow(inaug.list)),
                   rep("nomin", nrow(nomin.list)),
                   rep("farewell", nrow(farewell.list)))
speech.url=rbind(inaug, nomin, farewell)
speech.list=cbind(speech.list, speech.url)

# Loop over each row in speech.list
speech.list$fulltext=NA
for(i in seq(nrow(speech.list))) {
  text <- read_html(speech.list$urls[i]) %>% # load the page
    html_nodes(".displaytext") %>% # isloate the text
    html_text() # get the text
  speech.list$fulltext[i]=text
  # Create the file name
  filename <- paste0("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/data/fulltext/", 
                     speech.list$type[i],
                     speech.list$File[i], "-", 
                     speech.list$Term[i], ".txt")
  sink(file = filename) %>% # open file to write 
  cat(text)  # write the file
  sink() # close the file
}

colnames(speech.list)[1] = "President"
speech1=paste(readLines("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/data/fulltext/SpeechDonaldTrump-NA.txt", 
                  n=-1, skipNul=TRUE),
              collapse=" ")
speech2=paste(readLines("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/data/fulltext/SpeechDonaldTrump-NA2.txt", 
                  n=-1, skipNul=TRUE),
              collapse=" ")
speech3=paste(readLines("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/data/fulltext/PressDonaldTrump-NA.txt", 
                  n=-1, skipNul=TRUE),
              collapse=" ")

Trump.speeches=data.frame(
  President=rep("Donald J. Trump", 3),
  File=rep("DonaldJTrump", 3),
  Term=rep(0, 3),
  Party=rep("Republican", 3),
  Date=c("August 31, 2016", "September 7, 2016", "January 11, 2017"),
  Words=c(word_count(speech1), word_count(speech2), word_count(speech3)),
  Win=rep("yes", 3),
  type=rep("speeches", 3),
  links=rep(NA, 3),
  urls=rep(NA, 3),
  fulltext=c(speech1, speech2, speech3)
)

colnames(speech.list)[1] = "President"
speech.list=rbind(speech.list, Trump.speeches)


# Step 4: data Processing --- generate list of sentences


sentence.list=NULL
for(i in 1:nrow(speech.list)){
  sentences=sent_detect(speech.list$fulltext[i],
                        endmarks = c("?", ".", "!", "|",";"))
  if(length(sentences)>0){
    emotions=get_nrc_sentiment(sentences)
    word.count=word_count(sentences)
    # colnames(emotions)=paste0("emo.", colnames(emotions))
    # in case the word counts are zeros?
    emotions=diag(1/(word.count+0.01))%*%as.matrix(emotions)
    sentence.list=rbind(sentence.list, 
                        cbind(speech.list[i,-ncol(speech.list)],
                              sentences=as.character(sentences), 
                              word.count,
                              emotions,
                              sent.id=1:length(sentences)
                              )
    )
  }
}

sentence.list=
  sentence.list%>%
  filter(!is.na(word.count)) 

corpus.list=sentence.list[2:(nrow(sentence.list)-1), ]
sentence.pre=sentence.list$sentences[1:(nrow(sentence.list)-2)]
sentence.post=sentence.list$sentences[3:(nrow(sentence.list)-1)]
corpus.list$snipets=paste(sentence.pre, corpus.list$sentences, sentence.post, sep=" ")
rm.rows=(1:nrow(corpus.list))[corpus.list$sent.id==1]
rm.rows=c(rm.rows, rm.rows-1)
corpus.list=corpus.list[-rm.rows, ]



docs <- Corpus(VectorSource(corpus.list$snipets))
#remove potentially problematic symbols
docs <-tm_map(docs,content_transformer(tolower))
#remove punctuation
docs <- tm_map(docs, removePunctuation)
#Strip digits
docs <- tm_map(docs, removeNumbers)
#remove stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
#remove whitespace
docs <- tm_map(docs, stripWhitespace)
#Stem document
docs <- tm_map(docs,stemDocument)


#LDA
dtm <- DocumentTermMatrix(docs)
rownames(dtm) <- paste(corpus.list$type, corpus.list$File,
                       corpus.list$Term, corpus.list$sent.id, sep="_")

rowTotals <- apply(dtm , 1, sum) #Find the sum of words in each Document

dtm  <- dtm[rowTotals> 0, ]
corpus.list=corpus.list[rowTotals>0, ]

#run LDA
#Set parameters for Gibbs sampling
burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

#Number of topics
k <- 15

#Run LDA using Gibbs sampling
ldaOut <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, 
                                                 seed = seed, best=best,
                                                 burnin = burnin, iter = iter, 
                                                 thin=thin))
#write out results
#docs to topics
ldaOut.topics <- as.matrix(topics(ldaOut))
table(c(1:k, ldaOut.topics))
write.csv(ldaOut.topics,file=paste("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/out/LDAGibbs",k,"DocsToTopics.csv"))

#top 6 terms in each topic
ldaOut.terms <- as.matrix(terms(ldaOut,20))
write.csv(ldaOut.terms,file=paste("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/out/LDAGibbs",k,"TopicsToTerms.csv"))

#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(ldaOut@gamma)
write.csv(topicProbabilities,file=paste("/Users/JingyiWang/Google Drive/5243 Data/GitHub/data/wk2-TextMining/out/LDAGibbs",k,"TopicProbabilities.csv"))

terms.beta=ldaOut@beta
terms.beta=scale(terms.beta)
topics.terms=NULL
for(i in 1:k){
  topics.terms=rbind(topics.terms, ldaOut@terms[order(terms.beta[i,], decreasing = TRUE)[1:7]])
}

topics.hash=c("Economy", "America", "Defense", "Belief", "Election", "Patriotism", "Unity", "Government", "Reform", "Temporal", "WorkingFamilies", "Freedom", "Equality", "Misc", "Legislation")
corpus.list$ldatopic=as.vector(ldaOut.topics)
corpus.list$ldahash=topics.hash[ldaOut.topics]

colnames(topicProbabilities)=topics.hash
corpus.list.df=cbind(corpus.list, topicProbabilities)


topic.plot=c(1, 13, 14, 15, 8, 9, 12)

speech.df=tbl_df(corpus.list.df)%>%filter(File=="JimmyCarter", type=="inaug")%>%select(sent.id, Economy:Legislation)
speech.df=as.matrix(speech.df)
speech.df[,-1]=replace(speech.df[,-1], speech.df[,-1]<1/15, 0.001)
speech.df[,-1]=f.smooth.topic(x=speech.df[,1], y=speech.df[,-1])
plot.stacked(speech.df[,1], speech.df[,topic.plot+1],
             xlab="Sentences", ylab="Topic share", main="JimmyCarter, Inaugural #Speeches")


speech.df=tbl_df(corpus.list.df)%>%filter(File=="GeorgeBush", type=="inaug")%>%select(sent.id, Economy:Legislation)
speech.df=as.matrix(speech.df)
speech.df[,-1]=replace(speech.df[,-1], speech.df[,-1]<1/15, 0.001)
speech.df[,-1]=f.smooth.topic(x=speech.df[,1], y=speech.df[,-1])
#plot.stacked(speech.df[,1], speech.df[,topic.plot+1],
       #      xlab="Sentences", ylab="Topic share", main="GeorgeBush, Inaugural #Speeches")

speech.df=tbl_df(corpus.list.df)%>%filter(File=="DonaldJTrump", type=="inaug")%>%select(sent.id, Economy:Legislation)
speech.df=as.matrix(speech.df)
speech.df[,-1]=replace(speech.df[,-1], speech.df[,-1]<1/15, 0.001)
speech.df[,-1]=f.smooth.topic(x=speech.df[,1], y=speech.df[,-1])
plot.stacked(speech.df[,1], speech.df[,topic.plot+1],
             xlab="Sentences", ylab="Topic share", main="GeorgeBush, Inaugural Speeches")

		

topic.plot=c(1, 13, 14, 15, 8, 9, 12)
print(topics.hash[topic.plot])

#These number are calculated by using above plot.stacked function, d1-d8 represents 8 presidents in chronical order 
d1 <- c(0.07495256, 0.14990513, 0.22485769, 0.29981026 ,0.37476282, 0.44971538, 0.52466795)
d2 <-c( 0.05862887,0.11725773,0.17588660,0.23451546,0.29314433,0.35177319,0.41040206)
d3 <-c(0.06260737, 0.12521474, 0.18782211, 0.25042948, 0.31303685, 0.37564422, 0.43825159)
d4 <-c(0.05993666,0.11987332, 0.17980997, 0.23974663, 0.29968329, 0.35961995, 0.41955660)
d5 <-c(0.07058961, 0.14117922, 0.21176883 ,0.28235843, 0.35294804 ,0.42353765, 0.49412726)
d6 <- c( 0.07222845, 0.14445690 ,0.21668535, 0.28891379, 0.36114224, 0.43337069, 0.50559914)
d7 <-c(0.0700362, 0.1400724, 0.2101086, 0.2801448 ,0.3501810, 0.4202172, 0.4902534)
d8 <-c(0.05991123, 0.11982247 ,0.17973370, 0.23964494 ,0.29955617, 0.35946741, 0.41937864)


a = matrix(NA, nrow = 8,ncol = 7)
a[1,] = d1;a[2,] = d2 ;a[3,] = d3  ;a[4,] = d4  ;a[5,] = d5  ;a[6,] = d6  ;a[7,] = d7 ;a[8,] = d8  

topicdf = data.frame(a)

topic.plot=c(1, 13, 14, 15, 8, 9, 12)

colnames(topicdf) = topics.hash[topic.plot]
president.list = c("RichardNixon" ,"JimmyCarter" ,"RonaldReagan" ,   "GeorgeBush","WilliamJClinton", "GeorgeWBush",   "BarackObama","DonaldJTrump")
rownames(topicdf) = president.list
topicdf$Party = c("Republican","Democratic","Republican","Republican","Democratic","Republican","Democratic","Republican")




topicdf2 <- topicdf %>% group_by(Party) %>% summarise_each(funs(mean))
colnames(topicdf2)<- c("Party",topics.hash[topic.plot])

new = c(topicdf2$Economy,topicdf2$Equality,topicdf2$Misc,topicdf2$Legislation,topicdf2$Government,topicdf2$Reform,topicdf2$Freedom)


topicdf3 = data.frame(value  = new,type = rep(topics.hash[topic.plot], each = 2),
                      Party = rep(c("Republican", "Democratic"),7))


library("ggplot2")

 ggplot(topicdf3,aes(fill = Party, y = value, x = factor(type))) +
    geom_bar(position="dodge", stat="identity",width=0.5)+
   scale_fill_manual(values=c("#1F78B4", "#E31A1C")) + 
  theme(axis.text.x=element_text(angle=60, hjust=1,color="#993333",face="bold"))+
  labs(title = "Average frequency presidents adresse 7 topics", x= "Topics",size = 3) 
```
Finally we look at a cluster plot of the topics in Inaugural Speeches. Topics change over years, and the presidents in the recent 50 years cover similar topics compared to presidents from the old times. It's noticable that President Donald Trump and George Bush covered topics relatively different from the other recent presidents. It's also interesting they are both presidents of the Republican party. All presidents from the Democratic Party(in my analysis) cover similar topics.
```{r echo = FALSE}
sel.comparison=c("DonaldJTrump","JohnMcCain", "GeorgeBush", "MittRomney", "GeorgeWBush",
                 "RonaldReagan","AlbertGore,Jr", "HillaryClinton","JohnFKerry", 
                 "WilliamJClinton","HarrySTruman", "BarackObama", "LyndonBJohnson",
                 "GeraldRFord", "JimmyCarter", "DwightDEisenhower", "FranklinDRoosevelt",
                 "HerbertHoover","JohnFKennedy","RichardNixon","WoodrowWilson", 
                 "AbrahamLincoln", "TheodoreRoosevelt", "JamesGarfield", 
                 "JohnQuincyAdams", "UlyssesSGrant", "ThomasJefferson",
                 "GeorgeWashington", "WilliamHowardTaft", "AndrewJackson",
                 "WilliamHenryHarrison", "JohnAdams")
presid.summary=tbl_df(corpus.list.df)%>%
  filter(type=="inaug", File%in%sel.comparison)%>%
  select(File, Economy:Legislation)%>%
  group_by(File)%>%
  summarise_each(funs(mean))

presid.summary=as.data.frame(presid.summary)
rownames(presid.summary)=as.character((presid.summary[,1]))
km.res=kmeans(scale(presid.summary[,-1]), iter.max=200,
              5)
fviz_cluster(km.res, 
             stand=T, repel= TRUE,
             data = presid.summary[,-1],
             show.clust.cent=FALSE)
```

###Conclusion
For the 8 recent presidents, their inaugural speeches cover very similar topics but still differ by party. And when we take a closer look at the words presidents used in speeches, it seems like the contents differ by parties and match the party's ideologies. 




